Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-16 paper/structureScene.tex
Subtitle in scattering section
Discussion is relevant to any audio signals, not just auditory
scenes.

\subsection{Invariance and stability in acoustic scenes}
The notion of invariance to time-shifting plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their original class memberships.
To discard this superfluous source of variability, signals can be mapped to a time-shifting invariant feature space before training the classifier, eliminating the need for this classifier to explicitly learn this invariance and increasing the robustness of its predictions.

>>>>

\subsection{Invariance and stability in audio signals}
The notion of invariance to time-shifting plays an essential role in acoustic scene similarity retrieval as well as acoustic scene classification.
Indeed, recordings may be shifted locally without affecting their original class memberships.
To discard this superfluous source of variability, signals can be mapped to a time-shifting invariant feature space before training the classifier, eliminating the need for this classifier to explicitly learn this invariance and increasing the robustness of its predictions.
